Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-09 reviews/reviewer2-response.md

We did try computing "difference" plots, but these were a bit noisy and were
difficult to interpret.

>Wouldnt this have to be a number of complete revolutions?

It virtually is--6.03 revolutions technically, but the additional 0.03
revolutions should not have any appreciable effect on the statistics.

>Is this relevant to the paper [the performance curves]?

This is a valid point. If the reviewer thinks the paper would read okay without
this figure, we would be willing to remove it.

>Why so long [the computational domain]?

We did not perform a mesh dependence study for domain length---only for the
resolution. Since this is a RANS model, the large scale turbulent structures do
not advect downstream like they would in an LES model, as the 3-D vorticity
contours show.

### 2016-10-09 paper.tex
Discuss mesh resolution per rev 2
SST divergence for smaller time steps is unknown

Time step dependence was evaluated using the 2-D $N_x=70$ grid, the results from
which are shown in Figure~\ref{fig:2d-br-verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum
at $\Delta t = 0.002$ s, with some divergence for smaller time steps. The local
minimum was chosen as the final time step to run the simulations. Note that the
SST model's convergence behavior may be due to its specific implementation in
OpenFOAM, and not indicative of the nature of the model equations. Verification
studies for CFTs with this level of detail in the literature are not common,
though the final time step is comparable to others \cite{Balduzzi2016}. Note
that while in general there may be a coupling between necessary spatial and
temporal resolution, these values were arrived at iteratively, i.e., the spatial
dependence was varied with the chosen time step, and vice versa, such that there
was one independent variable for each parameter sweep.

>>>>

Time step dependence was evaluated using the 2-D $N_x=70$ grid, the results from
which are shown in Figure~\ref{fig:2d-br-verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum
at $\Delta t = 0.002$ s, with some divergence for smaller time steps, the reason
for which is unknown. The local minimum was chosen as the final time step to run
the simulations. Note that the SST model's convergence behavior may be due to
its specific implementation in OpenFOAM, and not indicative of the nature of the
model equations. Verification studies for CFTs with this level of detail in the
literature are not common, though the final time step is comparable to others
\cite{Balduzzi2016}. Note that while in general there may be a coupling between
necessary spatial and temporal resolution, these values were arrived at
iteratively, i.e., the spatial dependence was varied with the chosen time step,
and vice versa, such that there was one independent variable for each parameter
sweep.
